\papertitle

### 2012-10-12 manuscript.tex
Added platform footnotes, ornithopter section references,  and experiment section.

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
% humphrey
In order to conduct these experiments on cooperation we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit I-Bird 
RC flyer power train and clap-fling wings [FOOTNOTE], the H$^2$Bird's wingspan is 26.5 
cm and it has a flight weight of 13 grams. A tail propeller and 
servo-controlled tail elevator provide control in the yaw and pitch axes. The 
on-board electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery [FOOTNOTE]. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed and can operate for approximately 10 minutes.
%TODO footnote for Silverlit I-Bird
%TODO footnote for ImageProc

@@

\begin{figure}[tb]
\centering
\includegraphics[height=150pt]{figures/h2bird_axes.pdf}
\caption{H$^2$Bird Ornithopter with flight control axes}
\label{fig:h2Bird_axes}
\end{figure}
%TODO label ibird drawing

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
acceptable tracking performance. We estimate the vehicle pose by naively
integrating the IMU, and use PID for controlling the vehicle.

One characteristic of the H$^2$Bird that separates it from other MAVs is the
high pitch angles achieved in routine flight. An Euler angle 
parametrization of the vehicle orientation suffers from singularities
around these high pitch angles, so we instead represent the vehicle orientation
with quaternions. An additional benefit of the quaternion representation is 
the ability to represent relative body and world coordinate angular displacements 
compactly with quaternion multiplication

Given a reference quaternion $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose. We then 
convert this error quaternion to an angle axis representation which is given
as an input to the PID controller.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%TODO ryan

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
%TODO cameron
To bound the performance of our system described in the previous sections, we
determined the feasible set of initial conditions that resulted in successful
window traversal. We then conducted experiments to calculate the success rate
both within the feasible region and on the edges of the feasible region. The
following sections detail how we calculated the feasible and infeasible
regions using system identification and present the results of our
experimental trials.

>>>>

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
% humphrey
In order to conduct these experiments on cooperation we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit I-Bird 
RC flyer power train and clap-fling wings\footnote{\url{http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird's wingspan is 26.5 cm and it has a flight weight of 13 grams. A tail propeller and 
servo-controlled tail elevator provide control in the yaw and pitch axes. The 
on-board ImageProc 2.4 electronics package consists of a 40 MIPS microprocessor, 
6 DOF IMU, IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by 
a 90 mAh lithium polymer battery\footnote{Expand! Accredit it to Stan Baek!}. In routine flight, the H$^2$Bird 
averages 1.2 m/s ground speed and can operate for approximately 10 minutes.
%TODO footnote for Silverlit I-Bird
%TODO footnote for ImageProc

@@

\begin{figure}[tb]
\centering
\includegraphics[height=150pt]{figures/h2bird_axes.pdf}
\caption{H$^2$Bird Ornithopter with flight control axes}
\label{fig:h2Bird_axes}
\end{figure}
%TODO check ibird labels

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
acceptable tracking performance. We estimate the vehicle pose by naively
integrating the IMU, and use PID for controlling the vehicle.
%TODO Cite Stan paper
One behavior of the H$^2$Bird that separates it from other MAVs is the
high pitch angles achieved in routine flight. Baek\cite{baek:tracking} 
demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation. However, Euler angles suffer from singularities
around high pitch angles, so we instead represent the vehicle orientation
with quaternions. An additional benefit of the quaternion representation is 
the ability to represent relative body and world coordinate angular displacements 
compactly with quaternion multiplication

Our implementation of quaternion-based control is similar to Knoebe's\cite{knoebe:quatcontrol}: 
Given a reference quaternion $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose. We then 
convert this error quaternion to an angle axis representation which is given
as an input to the PID controller.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%TODO ryan
The task we chose to test our cooperative visual servoing system with is a 
simple target seeking one: the H$^2$Bird must fly through a specified obstacle,
in this case, a wooden frame meant to simulate a window. As the H$^2$Bird does
cannot detect the target on its own, it depends on remote guidance from the
base station. Ground truth data was collected via a motion capture system in
the test room. A sketch of the experimental setup is shown below in Figure 
~\ref{fig:experiment_cartoon}.

% TODO clarify or roll into paragraph
Trials were run as follows:
\begin{enumerate}
\item The window is identified by a user. 
\item The H$^2$Bird is released in view of the camera by hand.
\item The H$^2$Bird attempts to fly to the window with remote guidance from
the base station.
\end{enumerate}

% TODO Fill in test # per battery
Variations in the H$^2$Bird hand launch cause the system to respond differently 
for otherwise identical initial initial conditions. In addition, the H$^2$Bird 
battery was changed approximately every [10] tests, adding more variation to
the H$^2$Bird performance by affecting the motor power output. The effects of 
these noisy factors is considered in Section ~\ref{sec:performance}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
\label{sec:performance}
%TODO cameron
To bound the performance of our system described in the previous sections, we
determined the feasible set of initial conditions that resulted in successful
window traversal. We then conducted experiments to calculate the success rate
both within the feasible region and on the edges of the feasible region. The
following sections detail how we calculated the feasible and infeasible
regions using system identification and present the results of our
experimental trials.
